Rasterizing prodution per each region

### 2021-04-26 marine/last_step_rasterize/bivalve_rasterize_production.Rmd
wrote READMEs and cleaned up organization

library(here)
library(dplyr)
library(sf)
library(raster)
library(mapview)

@@

>>>>

library(here)
library(dplyr)
library(sf)
library(raster)
library(mapview)
library(tidyverse)

@@

farms_sf_prod <- st_as_sf(farms_prod)

## write the production data so that we can use it for the nutrient layer. 
st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/bivalve/prod_data_by_cell_iso3c.shp")

### 2021-04-26 marine/last_step_rasterize/crustaceans_rasterize_production.Rmd
wrote READMEs and cleaned up organization

data <- read_csv("marine/output/all_marine_farms.csv") %>% 
  st_as_sf(., 
           coords = c("lon", "lat"),
           crs = crs(food_raster), 
           agr = "constant")

all_farms <- list.files("data/temp_data/", pattern = "rds$", full.names = TRUE) %>% 
  map_df(., readRDS) %>% 
  rename(iso3c = iso3) %>% 
  mutate(source = "modeled") %>% 
  #left_join(tonnage_per_farms)
  rbind(data %>% mutate(source = "real"))

@@

# some annoying mismatches due to raster resolution. Fix these

@@

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% c("CHN:HKG", "CHN:MAC"), "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% c("CHN:HKG", "CHN:MAC"), "China", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "MMR:THA", "MMR", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "MMR:THA", "Myanmar", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "VNM:KHM", "VNM", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "VNM:KHM", "Vietnam", NAME_0))

@@

test <- farms_prod %>%
  dplyr::group_by(iso3c) %>%
  dplyr::summarize(total_tonnes = sum(tonnes_per_farm, na.rm=TRUE)) %>%
  left_join(fao, by = "iso3c") %>%
  mutate(difference = fao_tonnes_production - total_tonnes)

>>>>

data <- read_csv("marine/output/all_marine_farms.csv") %>% 
  st_as_sf(., 
           coords = c("lon", "lat"),
           crs = crs(food_raster), 
           agr = "constant") %>%
  mutate(source = "real")

all_farms <- list.files("data/temp_data/temp_marine_final", pattern = "rds$", full.names = TRUE) %>% 
  map_df(., readRDS) %>% 
  rename(iso3c = iso3) %>% 
 dplyr::mutate(source = "modeled") %>% 
  #left_join(tonnage_per_farms)
  rbind(data)

@@

# some annoying mismatches due to raster resolution. Fix these
# CHN:HKG
# CHN:MAC

@@

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% c("CHN:HKG", "CHN:MAC"), "CHN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% c("CHN:HKG", "CHN:MAC"), "China", NAME_0))

@@

test <- farms_prod %>%
  st_drop_geometry() %>%
  dplyr::group_by(iso3c) %>%
  dplyr::summarize(total_tonnes = sum(tonnes_per_farm, na.rm=TRUE)) %>%
  left_join(fao, by = "iso3c") %>%
  mutate(difference = fao_tonnes_production - total_tonnes)

### 2021-04-26 marine/last_step_rasterize/salmon_rasterize_production.Rmd
wrote READMEs and cleaned up organization

@@

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CAN:USA", "CAN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CAN:USA", "Canada", NAME_0)) %>%
  mutate(NAME_1 = ifelse(check %in% "CAN:USA", "New Brunswick", NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "USA:CAN", "USA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "USA:CAN", "United States", NAME_0)) %>%
  mutate(NAME_1 = ifelse(check %in% "USA:CAN", "Maine", NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "FIN:ALA", "FIN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "FIN:ALA", "Finland", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "FIN:RUS", "FIN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "FIN:RUS", "Finland", NAME_0))

>>>>

# CAN:USA
# FIN:ALA
# FIN:RUS
# RUS:CHN
# USA:CAN

@@

farms_sf_correct <- farms_sf %>%
  mutate(GID_0 = as.character(GID_0)) %>%
  mutate(NAME_0 = as.character(NAME_0)) %>%
  mutate(NAME_1 = as.character(NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "CAN:USA", "CAN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "CAN:USA", "Canada", NAME_0)) %>%
  mutate(NAME_1 = ifelse(check %in% "CAN:USA", "New Brunswick", NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "USA:CAN", "USA", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "USA:CAN", "United States", NAME_0)) %>%
  mutate(NAME_1 = ifelse(check %in% "USA:CAN", "Maine", NAME_1)) %>%
  mutate(GID_0 = ifelse(check %in% "FIN:ALA", "FIN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "FIN:ALA", "Finland", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "FIN:RUS", "FIN", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "FIN:RUS", "Finland", NAME_0)) %>%
  mutate(GID_0 = ifelse(check %in% "RUS:CHN", "RUS", GID_0)) %>%
  mutate(NAME_0 = ifelse(check %in% "RUS:CHN", "Russia", NAME_0))

### 2021-04-26 marine_mapping_OLD_v1/bivalve/food_pressures/bivalve_disturbance/bivalve_disturbance.Rmd
wrote READMEs and cleaned up organization

write.csv(bivalve_w_l_final, file.path("aquaculture/marine/bivalve/bivalve_disturbance/data/weight_length_relationships.csv"), row.names = FALSE)

@@

```{r}
# read in spp specific country bivalve data: 
bivalve_spp <- read_csv(file.path("aquaculture/marine/bivalve/bivalve_farms/data/fao_mariculture_bivalve_taxa_production.csv"))

## read in family information
spp_families <- read_csv(file.path("aquaculture/marine/STEP1_species_groups/int/marine_groups.csv")) %>%
  dplyr::filter(year == 2017) %>%
  dplyr::select(species, family) %>%
  distinct()

>>>>

write.csv(bivalve_w_l_final, file.path("marine/bivalve/food_pressures/bivalve_disturbance/data/weight_length_relationships.csv"), row.names = FALSE)

@@

```{r}
# read in spp specific country bivalve data: 
bivalve_spp <- read_csv(file.path("marine/bivalve/bivalve_farms/data/fao_mariculture_bivalve_taxa_production.csv"))

## read in family information
spp_families <- read_csv(file.path("marine/STEP1_species_groups/int/marine_groups.csv")) %>%
  dplyr::filter(year == 2017) %>%
  dplyr::select(species, family) %>%
  distinct()

### 2021-04-26 marine_mapping_OLD_v1/bivalve/food_pressures/bivalve_nutrient/bivalve_nutrient.Rmd
wrote READMEs and cleaned up organization

```{r}
fao <- read.csv(here("aquaculture/data/fao_mariculture_clean.csv")) %>%
  filter(environment %in% c("Marine", "Brackishwater"))

## Read in fao data and get a species list for salmon
species_list <- read.csv(here("aquaculture/marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
  distinct(species, aq_group)

taxon_list <- read.csv(here("aquaculture/marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
  distinct(species, Taxon_code, aq_group)

>>>>

```{r}
fao <- read.csv(here("data/fao_aquaculture_clean.csv")) %>%
  filter(environment %in% c("Marine", "Brackishwater"))

## Read in fao data and get a species list for salmon
species_list <- read.csv(here("marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
  distinct(species, aq_group)

taxon_list <- read.csv(here("marine/STEP1_species_groups/int/marine_groups.csv"))  %>%
  distinct(species, Taxon_code, aq_group)

### 2021-04-26 marine_mapping_OLD_v1/tuna/tuna_farms/STEP3_rasterize_production.Rmd
wrote READMEs and cleaned up organization

data <- read_csv("marine/output/all_marine_farms.csv") %>% 
  st_as_sf(., 
           coords = c("lon", "lat"),
           crs = crs(food_raster), 
           agr = "constant")

all_farms <- list.files("data/temp_data/temp_marine_final", pattern = "rds$", full.names = TRUE) %>% 
  map_df(., readRDS) %>% 
  rename(iso3c = iso3) %>% 
  mutate(source = "modeled") %>% 
  #left_join(tonnage_per_farms)
  rbind(data %>% mutate(source = "real"))

tuna_farms <- all_farms %>%
  dplyr::filter(type == "tuna")

mapview(tuna_farms)
```

@@

tuna_farms$reg_id <- raster::extract(gadm_latlon, tuna_farms)

farms_sf <- tuna_farms %>%
  left_join(gadm_codes, by="reg_id") %>%
  dplyr::mutate(NAME_1 = as.character(NAME_1))

@@

test <- farm_production %>%
  st_drop_geometry() %>%
  dplyr::group_by(iso3c) %>%
  dplyr::summarize(total_tonnes = sum(tonnes_per_farm, na.rm=TRUE)) %>%
  left_join(fao, by = "iso3c") %>%
  mutate(difference = fao_tonnes_production - total_tonnes)

@@

## write the production data so that we can use it for the nutrient layer. 
st_write(farms_sf_prod, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/tuna/prod_data_by_cell_iso3c.shp")

@@

write_csv(tuna_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/tuna/tuna_farm_updated.csv")

>>>>

farms <- read.csv(here::here("marine/tuna/tuna_farms/data/global_tuna_farm_lat_lon.csv"))

farms_sf <-  st_as_sf(farms, coords = c("lon", "lat"), 
                 crs = crs(gadm_latlon), agr = "constant")

mapview(farms_sf)
```

@@

farms_sf$reg_id <- raster::extract(gadm_latlon, farms_sf)

farms_sf <- farms_sf %>%
  left_join(gadm_codes, by="reg_id") %>%
  dplyr::mutate(NAME_1 = as.character(NAME_1))

@@

test <- farm_production %>%
  dplyr::group_by(iso3c) %>%
  dplyr::summarize(total_tonnes = sum(tonnes_per_farm, na.rm=TRUE)) %>%
  left_join(fao, by = "iso3c") %>%
  mutate(difference = fao_tonnes_production - total_tonnes)

@@

## write the production data so that we can use it for the nutrient layer. 
st_write(farms_sf_prod, "marine/tuna/tuna_nutrient/prod_data_by_cell_iso3c.shp")

@@

write_csv(tuna_raster_df, "/home/shares/food-systems/Food_footprint/all_food_systems/dataprep/aquaculture/marine/tuna/tuna_farm.csv")
